Figures to insert in text

### 2018-04-08 Chapters/Chapter02.tex
comparison

\begin{enumerate}
    \item APL implementation [59]

@@

@@

    \item The original hardware implementation developed by NASA [4]

@@

Let us analyse these.  The Connection Machine is obsolete.  APL, while influential, is not a mainstream language in science. The NASA implementation is hardware-based, hence not open-source.

The FPGA implementation by \citet{silva_reconfigurable_2004} has yielded a fast scan of hard locations, provided one has access to the proper hardware. Their article claims a four-fold speedup over assembly language; but it does not deal with parallel processing details.  For example, it is unclear whether there was more than a single thread running on the software implementation.  Note that the framework presented here is also able to reconfigure field-programmable gate arrays, through the OpenCL heterogeneous computing platform ability to interface with Hardware Description Language and hence, reconfigure FPGAs \citep{waidyasooriya2018design}.

>>>>

\begin{enumerate}
    \item The original hardware implementation developed by NASA [4]

@@

    \item APL implementation [59]

@@

@@

Let us analyse these.  The Connection Machine is obsolete.  The NASA implementation is hardware-based, hence not open-source.  APL, while influential, is not a mainstream language in science.

The FPGA implementation by \citet{silva_reconfigurable_2004} has yielded a fast scan of hard locations, provided one has access to the proper hardware. Their article claims a four-fold speedup over assembly language; but it does not deal with parallel processing details.  For example, it is unclear whether there was more than a single thread running on the software implementation.  Note that the framework presented here is also able to reconfigure field-programmable gate arrays, through the OpenCL heterogeneous computing platform ability to interface with Hardware Description Language and hence, reconfigure FPGAs \citep{waidyasooriya2018design, czajkowski_opencl_2012} for our tasks.

### 2018-04-08 Chapters/Chapter0A.tex
comparison

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{Bala Rajagopalan, Internet usenet rec.humor.funny, June 12 1989, `with apologies to non-cs types'.}. (QED)

>>>>

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-cs types': this wonderful result is from Bala Rajagopalan, posted on Internet Usenet rec.humor.funny in June 12 1989.}. (QED)
